Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-16 paper/paper.tex
fix seeds table

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and other suites.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TS-39 & \cite{ecma262-conformance-suite} & \Fix{-} \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\Igor{  
  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}
}

@@

    23 & 7/12 & \crossmark & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\

@@

This section shows results obtained with our
infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42
days. So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that 8 of the 19 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and other suites.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\Igor{
  No total, foram obtidos \nofuzzingAll{} warnings, sendo estes \nofuzzingHigh{}
  com priority HI e \nofuzzingLow{} do grupo LO. Nos analisamos cuidadosamente
  cada warning reportado pela ferramenta, a fim de encontrar bugs reais nos engenhos
  javascript. Nosso estudo revelou que dos \nofuzzingHigh{} do grupo HI, 
  \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
  \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).

  A diversidade de suites de testes influencia na busca de bugs nao descobertos
  pelo proprio projeto do engenhos. Por exemplo, cerca de \Fix{62} warnings 
  foram obtidos do repositorio da Mozilla, 12 na suite do JerryScript, 
  9 sao do WebKit e 2 sao do V8 e Duktape, respectivamente. 
  Os warnings encontrados em sua maioria sao dos engenhos do 
  Chakra e do JavascriptCore.

  A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}

  % Nosso estudo revelou que dos \tableBugsNum{} bugs reportados pelo nosso time, 
  % apenas \Fix{10} nao foram fuzzados \Fix{43.4\%},
  % Apesar do engenhos do V8 e SpiderMonkey
  % serem os mais robustos em relacao aos demais, tambem 
  % foram encontrados warnings nestes engenhos, porem
}

@@

    23 & 7/12 & \crossmark & Chakra & Dup (\#10) & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
    24 & 7/17 & \crossmark & SpiderMonkey & New & \href{https://bugzilla.mozilla.org/show_bug.cgi?id=1476321}{\#1476321} & HI & JerryScript\\

@@

This section shows results obtained with our
infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42
days. So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. 
\Igor{
The bugs reported on Chakra's bug tracker was defined as confirmed, 
however the bugs are included on a milestone for the next release
following an internal priority.
}
As of now, we did not find any new bug on SpiderMonkey and V8; 
the bugs we found were duplicates and were not reported. Finally, it is
worth noting that \Fix{11 of the 19} JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.
